### 2020-05-25 case-studies.tex
tweaked text for grading case study

Livelits are able to address this tension. 
Fig.~\ref{fig:grading} shows a Hazel program where the user has:\todo{label each of these 1-5 in figure?}{}
\begin{enumerate}
\item directly recorded numeric \li{grades} for each student using a livelit, \li{\$dataframe}, that implements a tabular spreadsheet-like interface suitable for this purpose, 
\item programmatically computed the overall \li{averages} for each student by calling a function, \li{compute_averages}, defined in a library (not shown), 
\item determined the \li{cutoffs} between letter grades by directly manipulating a livelit that provides a drag-and-drop interface superimposed on a visualization of the grade distribution, 
\item programmatically assigned letter grades to each student based on the cutoffs determined by the livelit in (3) by calling a library function, \li{assign_grades}, and 
\item formatted the final grade assignments in a manner suitable for submission to a university system by calling another library function, \li{format_for_university}.
\end{enumerate}

\subsubsection{Overview}\label{sec:live-grading-overview}
Talk about the scenario

Live matrix: what is a matrix structurally? (data frame? list of lists?) + how does liveness work
+ overview of hygiene guarantees

Grade cutoffs: how does it work wrt liveness? (do we use a parameter here instead of a splice?) -- 
focus on domain-specific benefits here.

>>>>

Livelits are able to address this tension. 
Fig.~\ref{fig:grading} shows a Hazel program where the user has:\todo{label each of these 1-5 in figure?}{}
\begin{enumerate}
\item recorded numeric \li{grades} for each student using a livelit, \li{\$dataframe}, that implements a tabular user interface with support for live evaluation of the Hazel expressions in cells, 
\item programmatically computed the overall \li{averages} for each student by applying a function, \li{compute_averages}, defined in a library  (not shown) shared between multiple courses, 
\item determined reasonable \li{cutoffs} between letter grades by directly manipulating a livelit that offers a domain-specific drag-and-drop interface superimposed on a live visualization of the grade distribution 
(for the sake of space, we plot dots rather than a full histogram)\todo{should we do a histogram?}{}, 
\item programmatically assigned letter grades to each student based on the \li{cutoffs} determined in step (3) by calling another shared library function, \li{assign_grades}, 
\item formatted the final grade assignments in a manner suitable for submission to the university system by calling another shared library function, \li{format_for_university}.
\end{enumerate}

\subsubsection{Livelit Expansion} abc

\subsubsection{Typed Hygienic Splicing} abc

\subsubsection{Live Evaluation} abc
